Towards Practical First-Order Model Counting

### 2025-01-25 doc/paper/paper.tex
Move the section about three logics to the appendix

\todo[inline,caption={}]{
  For the entire paper:
  \begin{itemize}
    \item Finish adding DOIs or URLs to (non-book) references (and reformatting
          indentation) (and check reference formatting) (is the part about
          non-book references correct? Check previous proceedings) (maybe one
          more exception (graded logics)?) (I might be done)
    \item Sentence vs formula: be consistent and not confusing
    \item 15 pages excluding references
    \item Go through the rest of formatting instructions (in GTD)
    \item Make sure all the references (e.g., to examples are still valid)
    \item Maybe add extra references to subsections
  \end{itemize}
}
\section{Introduction}

@@

\subsection{The Three Logics of FOMC}\label{sec:threelogics}

% \begin{table*}[t]
%   \centering
%   \begin{tabular}{llclll}
%     \toprule
%     Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
%     \midrule
%     \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
%     \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
%     \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
%     \bottomrule
%   \end{tabular}
%   \caption{A comparison of the three logics used in FOMC\@. The
%     2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
%     sorts, support for constants, the maximum number of variables, and supported
%     quantifiers, respectively. The last column lists supported atoms in addition
%     to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
%     of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
%     latter depending on the domain size, $P$ represents a predicate, and $x$ and
%     $y$ are terms. }\label{tbl:logics}
% \end{table*}

@@

\todo[inline]{Expand the section, adding a more thorough and independent
  practical assessment}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item More benchmarks from NOT my work
    \item Make sure it's clear what the `raw' instances are
    \item Don't emphasise that the benchmarks come from my previous work
    \item Integrate the example below into the text, possibly moving irrelevant
          details (such as the formulas in other logics) to supplementary
          material
  \end{itemize}
}

@@

\todo[inline]{Shrink/restructure to fit into the margins}

@@

>>>>

\todo[inline,caption={}]{
  For the entire paper:
  \begin{itemize}
    \item Perhaps I can list the `authors contributed equally' statement as part
          of Funding. Check K's recent papers.
    \item Finish adding DOIs or URLs to (non-book) references (and reformatting
          indentation) (and check reference formatting) (is the part about
          non-book references correct? Check previous proceedings) (maybe one
          more exception (graded logics)?) (I might be done)
    \item Sentence vs formula: be consistent and not confusing
    \item 15 pages excluding references
    \item Go through the rest of formatting instructions (in GTD)
    \item Make sure all the references (e.g., to examples are still valid)
    \item Maybe add extra references to subsections
  \end{itemize}
}
\section{Introduction}

@@

@@

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Make sure it's clear what the `raw' instances are
    \item Don't emphasise that the benchmarks come from my previous work
    \item Integrate the example below into the text, possibly moving irrelevant
          details (such as the formulas in other logics) to supplementary
          material
  \end{itemize}
}

@@

\todo[inline]{Add lines of best fit (and comment on them) to expand this section
  a bit?}

@@

\appendix
\section{The Three Logics of FOMC}\label{sec:threelogics}

\begin{table}[t]
  \centering
  \begin{tabular}{llclll}
    \toprule
    Logic & Sorts & Constants & Variables & Quantifiers & Additional atoms\\
    \midrule
    \FO & one or more & \cmark & unlimited & $\forall$, $\exists$ & $x = y$\\
    \Ctwo & one & \xmark & two & $\forall$, $\exists$, $\exists^{= k}$, $\exists^{\le k}$, $\exists^{\ge k}$ & ---\\
    \UFO & one & \xmark & two & $\forall$ & $|P| = m$\\
    \bottomrule
  \end{tabular}
  \caption{A comparison of the three logics used in FOMC\@. The
    2\textsuperscript{nd}--5\textsuperscript{th} columns refer to: the number of
    sorts, support for constants, the maximum number of variables, and supported
    quantifiers, respectively. The last column lists supported atoms in addition
    to those of the form $P(\mathbf{t})$ for a predicate $P/n$ and an $n$-tuple
    of terms $\mathbf{t}$. Here: $k$ and $m$ are non-negative integers, with the
    latter depending on the domain size, $P$ represents a predicate, and $x$ and
    $y$ are terms. }\label{tbl:logics}
\end{table}

\todo[inline,caption={}]{
  \begin{itemize}
    \item Reference the table
    \item Delete references to this appendix (except for one place, probably in
          \cref{sec:experiments})
    \item Make sure the rest of the paper doesn't refer to these logics (or
          describe examples in them)
  \end{itemize}
}
